---
name: Eric Kim
surname:
position: "Emerging Marketing Professional"
phone: +1 (909) 270-X0058
www: yourwebsite.com
email: "kimeric344@gmail.com"
github: kim_eric222
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Motivated and detail-oriented marketing and analytics professional with a strong background in data interpretation, campaign strategy, and digital tools. Skilled in turning insights into action and communicating value across business teams.

# Technical Skills

- **Programming Languages:** R, Python, SQL, etc.  
- **Web Technologies:** HTML, CSS/SCSS, Quarto, CMS, Google Analytics, etc.

# Education

```{r}
tribble(
  ~ Degree,                                                  ~ Year,                         ~ College,                          ~ Institution,
  "B.S. in Business Administration (Marketing)",            "2019 – Expected Dec 2025",    "College of Business Administration", "Cal Poly Pomona",
  "High School Diploma",                                     "2016 – May 2020",             "N/A",                               "Diamond Bar High School"
) %>%
  detailed_entries(Degree, Year, College, Institution)

```

# Work Experience

```{r}
tribble(
  ~ Years,                     ~ Company,         ~ Duties,                                                                                                                                       ~ Title,
  
  "May 2024 – Jan 2025",       "Taberu Sushi",   list(
                         "Provided exceptional customer service by upselling daily specials and sake pairings, boosting average check value.",
                         "Educated guests on sushi varieties and pairing notes to enhance dining experiences.",
                         "Collaborated with kitchen staff to ensure timely preparation and delivery, maintaining <15-minute wait times.",
                         "Prepared and reset 15+ tables per shift, ensuring a clean and welcoming dining area.",
                         "Served omakase courses with personalized insights, improving guest satisfaction scores."
                       ), "Server",
  
  "Dec 2018 – Apr 2023",       "Tous Les Jours", list(
                         "Implemented product displays and layout changes that increased sales by 10%.",
                         "Led weekly inventory audits and budget forecasting to minimize stock discrepancies.",
                         "Maintained strong team communication in a high-volume environment, improving shift efficiency.",
                         "Assisted customers with purchases and resolved inquiries, enhancing overall store experience."
                       ), "Cashier"
) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why  = Duties
  )

```